*Prochlorococcus marinus* responses to light and oxygen

### 2024-03-08 Code/Manuscript_O2.Rmd
defined ATP

Metaproteomic datasets were obtained from the KM1128 entry in the BCO-DMO database [@saitoPeptidesTheirSpectral2018] accessed via the OPP in June 2019. Datasets contained:
	i) Peptide sequences and sample identification (ID) number;
	ii) Sample ID number, station, depth in meters below the surface the sample was collected at, best-hit BLASTP protein and species annotation and the corresponding Uniprot Entry number for the identified proteins;
	iii) Sample station depth and [O~2~].  
	The depth and [O~2~] were joined to peptide sequence and BLASTP annotations by ID number, depth and station using *tidyverse* package [@R-tidyverse] running under R v4.1.3 and RStudio v2023.06.0 [@RStudio]. The resulting merged dataset was filtered for those *Prochlorococcus* peptides, detected from 0 to 300 m below the surface, annotated as a subunit of *Prochlorococcus* chlorophyll binding proteins (Pcb); Photosystem II (PSII); Cytochrome b~6~f (Cytb~6~f);  Photosystem I (PSI); NADPH Dehydrogenase (NDH); Plastoquinol Terminal Oxidase (PTOX); Plastocyanin (PC); Ferredoxin (Fd); Ribulose-1,5-bisphosphate oxygenase (RUBISCO);  ATP Synthase;  FtsH proteases (FtsH) or ribosomes. Detected peptides were re-annotated for consistency and labelled, where feasible, according to strain, clade, subunit and protein complex. Full protein sequences corresponding to detected proteins were obtained from UniProt (https://www.uniprot.org/) and analyzed in Molecular Evolution and Genetic Analyses X (MEGAX) software  (https://www.megasoftware.net/). Sequences for proteins for each of the thirteen *Prochlorococcus* strains identified in the dataset were aligned with MUSCLE using UPGMA cluster method and a lambda of 24 with a -2.9 gap open penalty and 1.20 hydrophobicity multiplier.  Overall mean pairwise distance between protein sequences was determined using bootstrap variance estimation methods. Maximum likelihood phylogenetic trees were assembled using 1000 bootstrap replications with a 95% site coverage cut off. *Prochlorococcus* FtsH isoform identities, and functions, were inferred by sequence comparisons to the characterized four isoforms of FtsH protease of *Synechocystis* sp. PCC6803 [@bonisteelStrainSpecificDifferences2018].  Data for each strain was plotted against depth and  [O~2~] and sampling station.

>>>>

Metaproteomic datasets were obtained from the KM1128 entry in the BCO-DMO database [@saitoPeptidesTheirSpectral2018] accessed via the OPP in June 2019. Datasets contained:
	i) Peptide sequences and sample identification (ID) number;
	ii) Sample ID number, station, depth in meters below the surface the sample was collected at, best-hit BLASTP protein and species annotation and the corresponding Uniprot Entry number for the identified proteins;
	iii) Sample station depth and [O~2~].  
	The depth and [O~2~] were joined to peptide sequence and BLASTP annotations by ID number, depth and station using *tidyverse* package [@R-tidyverse] running under R v4.1.3 and RStudio v2023.06.0 [@RStudio]. The resulting merged dataset was filtered for those *Prochlorococcus* peptides, detected from 0 to 300 m below the surface, annotated as a subunit of *Prochlorococcus* chlorophyll binding proteins (Pcb); Photosystem II (PSII); Cytochrome b~6~f (Cytb~6~f);  Photosystem I (PSI); NADPH Dehydrogenase (NDH); Plastoquinol Terminal Oxidase (PTOX); Plastocyanin (PC); Ferredoxin (Fd); Ribulose-1,5-bisphosphate oxygenase (RUBISCO);  Adenosine triphosphate (ATP) Synthase;  FtsH proteases (FtsH) or ribosomes. Detected peptides were re-annotated for consistency and labelled, where feasible, according to strain, clade, subunit and protein complex. Full protein sequences corresponding to detected proteins were obtained from UniProt (https://www.uniprot.org/) and analyzed in Molecular Evolution and Genetic Analyses X (MEGAX) software  (https://www.megasoftware.net/). Sequences for proteins for each of the thirteen *Prochlorococcus* strains identified in the dataset were aligned with MUSCLE using UPGMA cluster method and a lambda of 24 with a -2.9 gap open penalty and 1.20 hydrophobicity multiplier.  Overall mean pairwise distance between protein sequences was determined using bootstrap variance estimation methods. Maximum likelihood phylogenetic trees were assembled using 1000 bootstrap replications with a 95% site coverage cut off. *Prochlorococcus* FtsH isoform identities, and functions, were inferred by sequence comparisons to the characterized four isoforms of FtsH protease of *Synechocystis* sp. PCC6803 [@bonisteelStrainSpecificDifferences2018].  Data for each strain was plotted against depth and  [O~2~] and sampling station.
